SMT-Boosted Security Types for Low-Level MPC

### 2025-11-11 toplas26/metaty.tex
checkpoint

Share types rely on SMT entailments via the \TirName{ShareEntails} and \TirName{PubEntails} rules,
which are not syntax directed. Our goal with the $\metaprot$ language is to automate share type
checking. To enable this we introduce \emph{share type annotations}

\begin{definition}
  Define $\Gamma \Vdash \stt : \sty$ iff $\Gamma,\true \Vdash \stt : \sty$ without the
  use of \TirName{ShareEntails} and \TirName{PubEntails}.
\end{definition}

>>>>

Share types rely on SMT entailments via the \TirName{ShareEntails} and
\TirName{PubEntails} rules, which are not syntax directed. Our goal
with the $\metaprot$ language is to automate share type checking. To
enable this we introduce \emph{share type annotations}. These
annotations allow programmer specification of properties that can be
verified as part of the Hoare triple analysis defined in Section
\ref{section-metahtrip} and that enable automated checking of types.

A fundamental component of the system is automated share type checking
of noninteractive computations.  We define an algorithmic, syntax
directed subset of noninteractive share typing as follows:
\begin{definition}
  Define $\Gamma \Vdash \stt : \sty$ iff $\Gamma,\true \Vdash \stt : \sty$ without the
  use of \TirName{ShareEntails} and \TirName{PubEntails}.
\end{definition}

The syntax of type annotations $\sta$ is defined in Figure
\ref{fig-sta}, which we extend the language of commands $\cmd$ to
include. Type annotations are of the form $e_1 \kwas e_2$, which
defines an SMT equivalence, and $e : \sty$ which are verified using
the automated $\Vdash$ typing judgement-- the key idea here being that
explicit equivalences can stand in for implicit \TirName{ShareEntails}
and \TirName{PubEntails} judgements. In the semantics type annotations
are interpreted as no-ops, and their integration in Hoare triple
derivations requires annotated equivalences to be included in
preconditions.  In an implementation, Hoare triple verification can be
conducted independently prior to type checking.

\subsubsection{Annotation Type Checking}
